Present bias in exploratory choice

### 2017-01-30 doc/cogsci2017/paper.tex
add missing citations on learned helplessness

Notably, though, while over-exploration does occur, a bias towards under-exploration in particular seems to be
observed across a wide range of domains. One of the most severe
expressions of under-exploration is learned helplessness, in which an organism
experiences the absence of contol over the environment, learns that the
environment is uncontrollable, and thus ceases to take actions that might allow
it to discover that it can in fact exert control. Learned helplessness has been proposed to
underly most notably depression \citep{Abramson1978, Abramson1989} but also
problems ranging from difficulties in school CITE to poverty CITE.
While the cognitive appraisal of experienced events affects the development of
learned helplessness \citep{Abramson1978}, patterns of exploration clearly play
a role as well \citep{Huys2009, Teodorescu2014a}. In the case of depression,
interventions aimed at increasing the exploration of activities this might
produce a sense of pleasure and mastery have been found to be as effective as
those with a more cognitive orientation \citep{Jacobson1996}.

>>>>

Notably, though, while over-exploration does occur, a bias towards under-exploration in particular seems to be
observed across a wide range of domains. One of the most severe
expressions of under-exploration is learned helplessness, in which an organism
experiences the absence of contol over the environment, learns that the
environment is uncontrollable, and thus ceases to take actions that might allow
it to discover that it can in fact exert control. Learned helplessness has been proposed to
underly most notably depression \citep{Abramson1978, Abramson1989} but also
problems ranging from difficulties in school \citep{Diener1978} to poverty \citep{Evans2005}.
While the cognitive appraisal of experienced events affects the development of
learned helplessness \citep{Abramson1978}, patterns of exploration clearly play
a role as well \citep{Huys2009, Teodorescu2014a}. In the case of depression,
interventions aimed at increasing the exploration of activities this might
produce a sense of pleasure and mastery have been found to be as effective as
those with a more cognitive orientation \citep{Jacobson1996}.
